Concentration of Maxima and Fundamental Limits in High-Dimensional Testing and Inference

### 2021-04-04 6.URS/URS.tex
rename files and folders according to the new structure
minor updates to Chapter 5 intro

Recall that the notion of uniform relative stability (URS) in Definition \ref{def:URS} is the key to the necessary conditions for exact support recovery 
established in Theorem \ref{thm:necessary}.
In this chapter, we provide a complete characterization of the class of URS Gaussian arrays in terms of a simple condition on their covariance structure.
The condition is as follows.

@@

\section{Ramsey's  theory and the structure of correlation matrices} 
\label{sec:Ramsey}
\input{5.URS/5.proofs-Ramsey.tex}

\section{URS implies UDD (Proof of the `only if' part of Theorem \ref{thm:Gaussian-weak-dependence})} 
\label{sec:URS=>UDD}
\input{5.URS/5.proofs-URS-UDD.tex}

\section{UDD implies URS (Proof of the `if' part of Theorem \ref{thm:Gaussian-weak-dependence})} 
\label{sec:UDD=>URS}
\input{5.URS/5.proofs-UDD-URS.tex}

\section{Numerical illustrations of exact support recovery under dependence}
\label{sec:URS-numerical}
\input{5.URS/5.numerical.tex}

>>>>

The notion of uniform relative stability (URS) in Definition \ref{def:URS} is the key to the necessary conditions for exact support recovery established in Theorem \ref{thm:necessary}.
In this chapter, we provide a complete characterization of the class of URS Gaussian arrays in terms of a simple condition on their covariance structure.
The condition is as follows.

@@

\section{Ramsey's  theory and the structure of correlation matrices} 
\label{sec:Ramsey}
\input{6.URS/6.proofs-Ramsey.tex}

\section{URS implies UDD (Proof of the `only if' part of Theorem \ref{thm:Gaussian-weak-dependence})} 
\label{sec:URS=>UDD}
\input{6.URS/6.proofs-URS-UDD.tex}

\section{UDD implies URS (Proof of the `if' part of Theorem \ref{thm:Gaussian-weak-dependence})} 
\label{sec:UDD=>URS}
\input{6.URS/6.proofs-UDD-URS.tex}

\section{Numerical illustrations of exact support recovery under dependence}
\label{sec:URS-numerical}
\input{6.URS/6.numerical.tex}
